Academic Advancement Advice: Author Articles as A.~A.

### 2018-03-15 trunk/citations/paper.tex
Needs proofreading, but maybe paper is done?

\section*{Abstract}
proof at last
    1\ \dirham

@@

This paper demonstrates that even within academic paper publishing
(which one could argue is obsessed with bias, prestigious conferences,
statistical language for formalizing objections, and status in the
K-12 hierarchy), this unfairness persists. Specifically, we find that
authors whose names come alphabetically earlier have higher citation
rates.

@@

\subsection{Relatable Computer Science Activities}

@@

Of course, inside \verb+HumanDate()+ I found a hasty patch I had
installed in A.D.~2014 called ``make logging not spit garbage on
mingw,'' suggesting that I had encountered and misdiagnosed this issue
in the past. Although this led me on a minor herring (e.g. is
\verb+__MINGW32__+ defined when cross-compiling for x86\_64?)
HumanDate just returned \verb+"mingw"+, so this really was a problem
with \verb+std::cerr+ crashing on the second thing printed with it
(i.e., with the returned \verb+ostream+).

@@

With \verb+cerr+ fixed, I could now easily see the original ``bug'',
which was a violated assumption: I expected (and \verb+CHECK+ed),
optimistically, that if the article had an {\tt author} field then the
author would be a string. I accounted for a missing author, an author
that was the empty string, but not {\tt author: null}. Thanks!

@@

These are mostly explained by being relatively rare words that appear
in extremely popular papers. For example, {\em folin} comes from an
1951 paper\cite{lowry1951protein} describing a procedure for using
this reagent, which I guess everyone who uses this technique cites
(Google scholar has this paper at 215,329 citations). {\em
  Power/knowledge} and {\em 1972-1977} both come from the title of a
Foucault book\cite{foucault1980power} with 31,590 citations.

@@

Even filtering for articles with \verb+"lang"+ explicitly set to
\verb+"en"+, I needed to manually create a blacklist of hundreds of
non-English words that commonly appeared in these article titles.
After a few rounds of blacklisting, some ``English'' articles started
to appear:

% 78371002.  5.3718855409784041e-027	53e9a089b7602d970296e0eb	Office Hours: Monday, Wednesday, Thursday and Friday 9:00 a.m. to 5:00 p.m.; Tuesday 9:00 a.m. to 6:45 p.m

% 78370998.  6.049184011159267e-027	56d81919dabfae2eee86f82a	Thomas Aquinas: Theologian By Thomas F. O'Meara, O.P. Notre Dame, University of Notre Dame Press, 1997. 302 pp. $16.95

The first is probably not the title of an article, although we can
agree that it is unlikely to be cited. The second is a bad entry, with
the entire citation packed into the title field. This book actually
does have 94 citations (or DOES IT?~\cite{o1997thomas}) on Google
Scholar and an Amazon Sales Rank of \#10,837 in {\em Christian
  Denominations \& Sects}. In order to prevent such data problems from
affecting our results, I then added a requirement that the article
have basic metadata (either a Digital DOI Identifier field or {\tt venue})
for it to be considered.

% 48654527.  5.8084026066881388e-026	56d918ecdabfae2eee6c6965	Eight contemporary poets : Charles Tomlinson, Donald Davie, R.S. Thomas, Philip Larkin, Ted Hughes, Thomas Kinsella, Stevie Smith, W.S. Graham

% 48654111.  1.7552310525171227e-019	53e99952b7602d9702190ac1	The 80th Birthday of Sir Henry Dale, O.M., G.B.E., M.D., F.R.C.P., F.R.S.: Salute to Henry Hallett Dale

% 48654054.  2.7492425189773547e-019	56d8ecc5dabfae2eee5b30f5	Narratives Unsettled: Digression in Robert Walser, Thomas Bernhard, and Adalbert Stifter by Samuel Frederick (review)

% 48552586.  5.0644175742872403e-019	56d9266ddabfae2eeebdd19a	Catherine Mowry LaCugna's Trinitarian Theology: III- The Ecumenical Implications of Catherine Mowry Lacugna's Trinitarian Theology

% 48552476.  1.7011818225031437e-018	56d85cd0dabfae2eee5cb5f4	Texts Illustrating the Causality of the Sacraments from William of Melitona, Assisi Bibl. Comm. 182, and Brussels Bibl. Royale 1542

% 48552391.  3.4094058998675013e-018	53e9bce1b7602d9704965e64	Shakespeare's Titus Andronicus and Bandello's Novelle as Sources for the Munera Episode in Spenser's Faerie Queene, Book 5, Canto 2

1. memorials for dead guys
2. reviews of books
3. articles not in english
4. broken citations

\largeskip
Of course, since these papers are all notable for being so extremely
uncitable, the true least citable papers are the next least citable,
according to this analysis.

@@

Adopting an all-'A' affect also advances articles. Although affairs
are abbreviated, adequate abstracts abound: Astronomy, asthma,
atmospheric acclimatization, autobiography, Azerbaijani accents,
acceleration, and abundant alternatives.

% arranged alphabetically.

Awesome!

strange authors:

u fucks
a a fucks

\bibliographystyle{IEEEtran}
% \bibliographycomment{} % nothing
\bibliography{paper}

>>>>

% \section*{Abstract}

@@

This paper demonstrates that even within academic paper publishing
(which one could argue is obsessed with bias, prestigious conferences,
statistical language for formalizing objections, and status in the
K-12 hierarchy), this unfairness persists. Specifically, we find that
authors whose names come alphabetically earlier have higher citation
rates. We also study some related subjects like, ``What is the most
uncitable paper?''

@@

\subsection{Relatable Computer Science Tale}

@@

First I checked for overfull hbox, but this was not the problem.
Of course, inside \verb+HumanDate()+ I found a hasty patch I had
installed in A.D.~2014 called ``make logging not spit garbage on
mingw,'' suggesting that I had encountered and misdiagnosed this issue
in the past. Although this led me on a minor herring (e.g. is
\verb+__MINGW32__+ defined when cross-compiling for x86\_64?)
HumanDate just returned \verb+"mingw"+, so this really was a problem
with \verb+std::cerr+ crashing on the second thing printed with it
(i.e., with the returned \verb+ostream+).

@@

With \verb+cerr+ fixed, I could now easily see the original ``bug'',
which was a violated assumption: I expected (and \verb+CHECK+ed),
optimistically, that if the article had an {\tt author} field then the
author would be a string. I accounted for a missing author, an author
that was the empty string, but not \verb+author: null+. Thanks!

@@

These are mostly explained by being relatively rare words that appear
in extremely popular papers. For example, {\em folin} comes from a
1951 paper\cite{lowry1951protein} describing a procedure for using
this reagent, which I guess everyone who uses this technique cites
(Google scholar has this paper at 215,329 citations). {\em
  Power/knowledge} and {\em 1972-1977} both come from the title of a
Foucault book\cite{foucault1980power} with 31,590 citations.

@@

Even filtering for articles with \verb+"lang"+ explicitly set to
\verb+"en"+, I needed to manually create a blacklist of hundreds of
non-English words (mostly Indonesian and Polish) that commonly
appeared in these article titles. After a few rounds of blacklisting,
some ``English'' articles started to appear:

\begin{quote}
 Office Hours: Monday, Wednesday, Thursday and Friday 9:00 a.m. to 5:00 p.m.; Tuesday 9:00 a.m. to 6:45 p.m \\
  \signed{(citation multiplier $5.37\!\times\!10^{-27}$)}
\end{quote}

\begin{quote}
	Thomas Aquinas: Theologian By Thomas F. O'Meara, O.P. Notre Dame, University of Notre Dame Press, 1997. 302 pp. \$16.95 \\
  \signed{(citation multiplier $6.05\!\times\!10^{-27}$)}
\end{quote}

The first is probably not the title of an article\cite{officehours},
although we can agree that it is unlikely to be cited. The second is
probably a bad entry, with the entire citation packed into the title
field. This book~\cite{o1997thomas} actually does have 94 citations
(or DOES IT?) on Google Scholar and an Amazon Sales Rank of \#10,837
in {\em Christian Denominations \& Sects}.\footnote{ On the other
  hand, the entry does have a different
  author\cite{stevenson2000thomas}, so it could possibly be a review
  of this book whose title is literally the string above, including
  the price?} In order to prevent such data problems from affecting
our results, I then added a requirement that the article have basic
metadata (either a Digital DOI Identifier field or {\tt venue}) for it
to be considered. There vast majority still appear to be broken
entries, but picking through the results I'm finally able to find what
appear to be actual articles:

\begin{quote}
  % 48654527.  5.8084026066881388e-026	56d918ecdabfae2eee6c6965
  Eight contemporary poets : Charles Tomlinson, Donald Davie, R.S. Thomas, Philip Larkin, Ted Hughes, Thomas Kinsella, Stevie Smith, W.S. Graham
  \signed{(citation multiplier $5.81\!\times\!10^{-26}$)}
\end{quote}

\begin{quote}
  % 48654111.  1.7552310525171227e-019	53e99952b7602d9702190ac1
  The 80th Birthday of Sir Henry Dale, O.M., G.B.E., M.D., F.R.C.P., F.R.S.: Salute to Henry Hallett Dale
  \signed{(citation multiplier $1.75\!\times\!10^{-19}$)}
\end{quote}

\begin{quote}
  % 48654054.  2.7492425189773547e-019	56d8ecc5dabfae2eee5b30f5
  Narratives Unsettled: Digression in Robert Walser, Thomas Bernhard, and Adalbert Stifter by Samuel Frederick (review)
  \signed{(citation multiplier $2.74\!\times\!10^{-19}$)}
\end{quote}

\begin{quote}
  % 48552586.  5.0644175742872403e-019	56d9266ddabfae2eeebdd19a
  Catherine Mowry LaCugna's Trinitarian Theology: III- The Ecumenical Implications of Catherine Mowry Lacugna's Trinitarian Theology
  \signed{(citation multiplier $5.06\!\times\!10^{-19}$)}
\end{quote}

\begin{quote}
  % 48552476.  1.7011818225031437e-018	56d85cd0dabfae2eee5cb5f4
  Texts Illustrating the Causality of the Sacraments from William of Melitona, Assisi Bibl. Comm. 182, and Brussels Bibl. Royale 1542
  \signed{(citation multiplier $1.70\!\times\!10^{-18}$)}
\end{quote}

\begin{quote}
  % 48552391.  3.4094058998675013e-018	53e9bce1b7602d9704965e64
  Shakespeare's Titus Andronicus and Bandello's Novelle as Sources for the Munera Episode in Spenser's Faerie Queene, Book 5, Canto 2
  \signed{(citation multiplier $3.41\!\times\!10^{-18}$)}
\end{quote}

The first is definitely a real article~\cite{bedient1974eight}---which
apparently has 95 citations on Google Scholar---so the estimate failed
us here. It's easy to see why it has such a bad score, though; it's
packed with people's names and initials, just like the scores of
uncited book reviews and other broken citations. The second is also a
real tribute to this Nobel prize winner~\cite{loewi195580th} with 5
citations that Google knows of. Again it contains names and
appelations that look like initials.

The third is a book review~\cite{holmes2015narratives} of a
book~\cite{frederick2012narratives} with itself only 11 citations
(makes sense, as the title contains three people's names) and indeed
has no citations that Google knows of, so it is a solid contender.
After that some theological
stuff~\cite{torrance2000catherine,lynch1957texts} each with 3
citations on Google, and another literary
analysis~\cite{fitzpatrick2005shakespeare} which has 2.

Lessons learned:
\begin{itemize}
\item Taking a noisy database of tens of millions of entries and then
  trying to dig through the bottom of the barrel for something
  ``funny'' or even ``interesting'' is tough going. Maybe this should
  have been obvious.
\item The least-cited works take on some recurring forms:
  \begin{itemize}
  \item Memorials for dead or old guys with lots of honorifics
  \item Articles with people's names in the title
  \item Reviews of books, or books about other literary work, or reviews of books about other literary work
  \item Articles about God stuff or God People
  \item Articles not in English
  \item Broken citations
  \item Combinations of the above.
  \end{itemize}
  Enterprising academics would do well to avoid such areas of research, in addition
  to using alphabetically early words and author names in their publications.

\item As one downside, this approach does not really work, given
  that several of these articles have a few actual citations upon
  comparing to another database.
\end{itemize}

\medskip
Of course, since these papers are all notable for being so extremely
uncitable, the true least citable papers are the {\bf next least
  citable}, according to this analysis. To avoid paradoxes, the
reader is discouraged from trying to reproduce these results.

@@

Adopting an all-'A' affect also advances articles. Although affairs
are abbreviated, adequate abstracts abound: Astronomy, asthma,
atmospheric acclimatization, autobiography, Azerbaijani accents,
acceleration, and abundant alternatives. After achieving academic
accomplishments, acknowledge A.A.'s {\it Academic Advancement Advice:
  Author Articles as A.~A}!

\section{Bibliography}

\bibliographystyle{IEEEtran}
\bibliography{paper}
